### 2020-06-30 conclusion.tex
修改

\section{Conclusion}
\label{sec-conclusion}
In this work we designed a holistic system for shoulder surfing on smartphone, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency. We proved that this threat towards screen privacy is imminent and can cause damage while undetected. It is our wish that this work can stur discussion in the field of screen privacy protection and proporgate defense mechanisms across critical mobile apps. Although this system proves to be highly efficient against unprotected screens, there are some simple methods to mitigate this unique threat while not cumbering the user. One of these defenses is displaying a dynamic background behind the characters, with a small protion of patterns colored similar to the texts. The constant changes will confuse most of the multi-frame SR algorithms, as they are often designed based on the assumption that all input images are reflections of the same scene. Other defence methods include active scanning for suspicious individuals, encrypted keyboards at password entry phases, etc.

>>>>

\section{Discussion}
\label{sec-discussion}
Although our shoulder surfing system proves to be highly efficient against unprotected screens, there are some simple methods to mitigate this unique threat while not cumbering the user.

\vspace{1mm}
\noindent
\textbf{Dynamic background.} Most multi-frame SR algorithms are designed based on the assumption that all input images are reflections of the same scene, and ours is not an exception. By deploying a dynamic background behind the characters, such as tiny dots and lines travelling slowly around the screen, we can construct a constantly changing scene that will confuse the multi-frame SR algorithms, and due to the blurriness of the images, these influencial elements cannot be easily removed. These dots do not need to be distinct or colored same as the the texts, as multi-frame SR algorithms function with tiny,pixel level differences between frames, making them especially sensitive to microscopic changes.

\textbf{Active scanning.} There are several works providing an active countermeasure against shoulder surfing threats with the naked eye. With front-facing cameras and face detection algorithms, the smartphone can constantly scan the surrounding passers-by and detect their gaze direction, and give a warning to the user when that gaze points at the screen. However, to the extent of our knowledge none of these works have included cameras into their detection scope, but we believe it's practical to implement such features.

\textbf{Adversarial machine learning methods.} In recent years we have discovered the weaknesses of neural networks and that inserting certain microscopic changes, undetectable to the human eye, to the pixels of an image will make it look different to a neural network. These methods fools the feature extraction phases of neural networks, so that SRPeek is also vulnerable to this attack. Theoretically, by exerting a pattern to the victim's screen, it can be captured by the attacker's camera and confuse its SR algorithms, but these remains to be implemented in our future work.

\section{Conclusion}
\label{sec-conclusion}
In this work we designed a holistic system, SRPeek, for shoulder surfing on smartphone, which serves as an up-to-date version of a threat model for shoulder surfing, and proved its efficiency. We proved that this threat towards screen privacy is imminent and can steal critical information, including personal texts or passwords, from long distances, thus escaping detection. It is our wish that this work can stur discussion in the field of screen privacy protection and proporgate defense mechanisms across critical mobile apps.

The core of SRPeek is a specially designed multi-frame SR network. With its innovative architecture this network outperforms other algorithms of the same field in our application. The design ideology enables this network to process higher levels of data integration ability while keeping a low calculation profile, and we believe the elements of this design can be used in other applications with large amounts of data, such as natural language processing or anomaly detection. Our model can also be used in OCR tasks when multiple images are avaliable, functioning as a preprocessor to improve the quality of the images and increase accuracy.

### 2020-06-30 design.tex
修改

Inside each layer $H_l$ there are 3 convolution layers $Conv_{1l}(\cdot)$, $Conv_{2l}(\cdot)$, $Conv_{3l}(\cdot)$ and 1 merging layer $Merge_l(\cdot)$, distributed as follows:

@@

\begin{enumerate}
\item The first input parameter of this layer, $x_i^{(l-1)}$, is passed through a convolution layer to extract features. Note that all three convolutional layers accept a single image(or its featuremaps from the last convolutional layer) as input, the convolutional process is repeated for all the images, and calculations within the same convolutional layer share the same group of parameters all the time (parameters denoted as $Param_{sl}$ for convolutional layer $Conv_{sl}, s=1,2,3$):

@@

\item The results of the previous step of all the images $\{a_1^{(l)},a_2^{(l)},...,a_n^{(l)}\}$ are then passed to the merging layer $Merge_l$ to generate $t$ groups of featuremaps. Suppose the results of $Conv_{1l}$ consists of $R$ channels:

@@

$$ b_{tr(p,q)}^{(l)} = \sum_{i=1}^{N} a_{ir(p,q)}^{(l)} e^{k_t a_{ir(p,q)}^{(l)}} /\sum e^{k_t a_{ir(p,q)}^{(l)}},$$
$$ p=1,2,...P, q=1,2,...Q, t=1,2,...T, r=1,2,...R $$

$P,Q$ denotes the height and width of the current images, (p,q) represent the pixel located at this coordinate, and $k_t$ is a set of fixed parameters shared in all the merging layers throughout the model, controlling the behavior of the merging process. Apparently, k=0 leads to averaging, k=${+\infty}$ leads to max operator and k=${-\infty}$ leads to min operator. We use T=5 and k=-1,-0.5,0,0.5,1 in our model, giving consideration to both consensuses (k=0,averaging) and prominent features(k=1, 'soft'max and k=-1, 'soft'min). these $T\times R$ channels $b_{tr}^{(l)}$ is the output of this merging layer $Merge_l$.

\item Separately, we pass the initial input images, $$x_i^{(0)}$$, or the second input parameter of $H_l$ into a convolutional layer$Conv_{2l}$, which is similar to $Conv_{1l}$ and process each image separately, also generating $N$ outputs with $R$ channels per output, denoted as $$c_ir^{(l)}, i=1,2,...N, r=1,2,...R$$:

@@

\item The data from step (2) and (3) are merged together, in that all the $T\times R$ channels of $b_{tr}^{(l)}$ are replicated N times and stacked with each one of the N outputs of $Conv_{2l}$, before these N outputs, each with $(T+1)\times R$ channels, are passed through the third convolutional layer $Conv_{3l}$. There are also N output of this convolutional layer, denoted as $d_i^{(l)}, i=1,2,...N$:

@@

\item If $l < L$, this is not the last layer, the N outputs of step (4) will be the output of layer $H_l$. Otherwise, as we need to present a single image $y$ as output, we add another merging and a common convolutional layer after $Conv_{3l}$. The merging layer is identical to the previous $Merge_l$, merging the N outputs $d_i^{(l)}$ into $T\times R$ channels $e_{tr}^{(l)}$, and a convolutional layer processes this $e_{tr}^{(l)}$ to generate a single channel of output $y$.

$$ \{e_{tr}^{(L)},t\in (1,T),r\in (1,R)\} = Merge`_{L}(\{d_i^{(L)},i\in (1,N)\})$$

$$ y = Conv`_{L}(\{e_{tr}^{(L)},t\in (1,T),r\in (1,R)\})$$

\end{enumerate}

@@

We implemented a holistic system for shoulder surfing, with the neural network as core, on a smartphone to verify the efficiency of our model. It iterates through the following steps: 
\begin{enumerate}

\item Input. Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen. Note that the zoom in step is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if avaliable, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range. This way information on the images will be more compact and easier to comprehend by neural networks.

\item Alignment. The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism. Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images. The images are also spun to make the text horizontal in the process. The screen is cropped out and the rest of the image abandoned.

\item Adjustment. The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network. The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size(and the zooming of step (1) will be adjusted accordingly).

\item Processing. As our network accepts only 9x9 patches, we will iteratively process all the overlapping 9x9 boxes among the input photo. For example, a 10x10 image will be four 9x9 patches, and a 11x11 image nine patches, etc(see Figure~\ref{fig-patches}. After carving a 9x9 patch at corresponding locations of each image, these patches are then processed by our multi-frame super resolution network, generating a single 36x36 image (4x upscaling). The input is RGB colored, while the output, as we are not interested in color, is black and white. When all patches are processed, their outputs are merged together. The overlapping pixels are thus processed: among all the outputs containing this pixel, we collect these values, remove outliers, and use their average as the result. In this way, we generate upscaled image segments of all the characters on the target screen, which are then inserted in one of the input images(roughly upscaled to encompass them, just for reference) and displayed to the attacker.

\begin{figure}
 \centering
    \includegraphics[width=0.5\textwidth]{./pic/patches.jpg}
    \caption{Illustration of overlapping patches the network process photos.}
    \label{fig-patches}
\end{figure}

\end{enumerate}

>>>>

Inside each layer $H_l$ there are 3 convolution layers $Conv_{1l}(\cdot)$, $Conv_{2l}(\cdot)$, $Conv_{3l}(\cdot)$ and 1 merging layer $Merge_l(\cdot)$.

@@

\vspace{1mm}
\noindent
\textbf{Conv1.} The first convolutional layer, $Conv1$, accepts the layer's first input parameter $x_i^{(l-1)}$ as input. Note that all three convolutional layers accept a single image(or its featuremaps from the last convolutional layer) as input, the convolutional process is repeated for all the images, and calculations within the same convolutional layer share the same group of parameters all the time (parameters denoted as $Param_{sl}$ for convolutional layer $Conv_{sl}, s=1,2,3$):

@@

\vspace{1mm}
\noindent
\textbf{Merge.} The results of the previous step of all the images $\{a_1^{(l)},a_2^{(l)},...,a_n^{(l)}\}$ are then passed to the merging layer $Merge_l$ to generate $t$ groups of featuremaps. Suppose the results of $Conv_{1l}$ consists of $R$ channels:

@@

$$ b_{tr(p,q)}^{(l)} = \sum_{i=1}^{N} a_{ir(p,q)}^{(l)} e^{k_t a_{ir(p,q)}^{(l)}} /\sum e^{k_t a_{ir(p,q)}^{(l)}},$$

where (p,q) represent the pixel at this coordinate, and $k_t$ is a set of fixed parameters shared in all the merging layers throughout the model, controlling the behavior of the merging process. Apparently, k=0 leads to averaging, k=${+\infty}$ leads to max operator and k=${-\infty}$ leads to min operator. We use T=5 and k=-1,-0.5,0,0.5,1 in our model, giving consideration to both consensuses (k=0,averaging) and prominent features(k=1, 'soft'max and k=-1, 'soft'min). these $T\times R$ channels $b_{tr}^{(l)}$ is the output of this merging layer $Merge_l$.

\vspace{1mm}
\noindent
\textbf{Conv2.} $Conv2$ is a replica of $Conv1$, processing the layer's second input parameter $x_i^{(0)}$, also generating $N$ outputs with $R$ channels per output, denoted as $c_ir^{(l)}, i=1,2,...N, r=1,2,...R$:

@@

\vspace{1mm}
\noindent
\textbf{Conv3.}The data from $Merge$ and $Conv2$ are merged together, in that all the $T\times R$ channels of $b_{tr}^{(l)}$ are replicated N times and stacked with each one of the N outputs of $Conv_{2l}$, before these N outputs, each with $(T+1)\times R$ channels, are passed through the third convolutional layer $Conv_{3l}$. There are also N output of this convolutional layer, denoted as $d_i^{(l)}, i=1,2,...N$:

@@

\vspace{1mm}
\noindent
\textbf{Output.}If $l < L$, this is not the last layer, the N outputs of step (4) will be the output of layer $H_l$. Otherwise, as we need to present a single image $y$ as output, we add another merging and a common convolutional layer after $Conv_{3l}$. The merging layer is identical to the previous $Merge_l$, merging the N outputs $d_i^{(l)}$ into $T\times R$ channels $e_{tr}^{(l)}$, and a convolutional layer processes this $e_{tr}^{(l)}$ to generate a single channel of output $y$.

$$ \{e_{tr}^{(L)},t\le T,r\le R\} = Merge'_{L}(\{d_i^{(L)},i\le N\})$$

$$ y = Conv'_{L}(\{e_{tr}^{(L)},t\le T,r\le R\} )$$

@@

We implemented a holistic system for shoulder surfing, with the neural network as core, on a smartphone to verify the efficiency of our model. It iterates through the following steps:

\vspace{1mm}
\noindent
\textbf{Input.} Under guidance of the attacker, The smartphone will zoom in, take focus, and take 20 images with burst mode of the target screen. Note that the zoom in step is only for easier interaction and focusing, and to utilize the telephoto lenses and optical zoom, if avaliable, as digital zooming do not put in any extra data; On traditional phones with only digital zooming, the photo-taking will be with 1x zoom, and on phones with optical zooming, 5x to 10x zoom, depending on the optical zooming range. This way information on the images will be more compact and easier to comprehend by neural networks.

\vspace{1mm}
\noindent
\textbf{Alignment.} The images are then aligned to mitigate the shifts between frames caused by hand tremor or movements from the lenses, as cameras with optical lenses will ocationally shift slightly across time due to the movements of its inner mechanism. Luckily, in our scenario the target is a glowing screen whose edges are easily distinguishable in most cases, and we use them as reference to align our images. The images are also spun to make the text horizontal in the process. The screen is cropped out and the rest of the image abandoned.

\vspace{1mm}
\noindent
\textbf{Adjustment.} The lines of text(or stuff differing from the background color of the screen) will be carved out for processing, to reduce the workload of the network. The characters are normally around 10x10 pixels in the photos, and the carved segments will leave 2 pixels of padding on all sides to avoid mutilating the character; A certain amount of error is allowed, but if the size of the text is too small or too large, the neural network will not be able to extract features normally, so the images will be zoomed to the right size(and the zooming of step (1) will be adjusted accordingly).

\vspace{1mm}
\noindent
\textbf{Processing.} As our network accepts only 9x9 patches, we will process all the 9x9 patches among the input photo and merge the results together. After carving a 9x9 patch at corresponding locations of each image, these patches are then processed by our multi-frame super resolution network, generating a single 36x36 image (4x upscaling). The input is RGB colored, while the output, as we are not interested in color, is black and white. When all patches are processed, their outputs are merged together. The overlapping pixels are thus processed: among all the outputs containing this pixel, we collect these values, remove outliers, and use their average as the result. In this way, we generate upscaled image segments of all the characters on the target screen, which are then inserted in one of the input images(roughly upscaled to encompass them, just for reference) and displayed to the attacker.

### 2020-06-30 implementation.tex
revision by cl
修改

\subsection{Experiment Setting}
\label{sec-experiment-setting}
In our experiment, we are forced to collect the training dataset on our own instead of using public datasets. Because of our unique application, to the best of our knowledge there is no publicly available image dataset built for shoulder-surfing. Modern network architectures work with naturally obtained images, e.g. ordinary photos, satellite images, scanned documents, YouTube videos, etc. where the images are well focused and captured within the imaging ability of the camera, with the objects of interest, e.g. the face or the printed word, at least visible to the naked eye. and we apply the SR algorithms to reduce noise and refine details, like repainting texture and refining edges. However, as emphasized above, in our application we face images that is extremely blurred and distorted, due to the extreme circumstances when the photos are taken, and it is impossible to tell from each single picture whether a stroke of a character really belongs here, as it's equally possible that this line is a distorted mixture of multiple lines or is a mutilated part of a longer stroke. Noise and details are not the main issue here, as we need only the facts, deeming it a victory if the neural network returns a noised, wrapped, but readable image. These are the reasons why our work does not choose datasets that are publicly available, and collect data by ourselves--as it will completely defeat the purpose if we turn to these datasets. And this also explains why we failed in trying to get comparable results with other SR architectures we use as baselines, as these networks are designed for another purpose and they hardly ever faced such distorted and blurred images.

The task of data collection is quite tedious, as we discovered that we need photos taken in all kinds of environments to train a robust network. We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them, so that in the testing phase the network has to recover characters that never appeared in the training dataset. Note that different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone model with a set of training images captured from it. When using smartphones with optical zoom, the images will shift slightly time after time even if we keep them completely still, so the aligning phases are still needed (this shifting is also beneficial in that it simulates normal hand tremors in real-life scenarios even if we fix the phone to a stand instead of holding it up throughout the data collection phase which can last several hours). There are no consistency between adjacent images, so we also shuffle the images to increase this shifting effect and increase the variety of the training data. %To reduce calculation and better align the images with the ground truth, in the training data collection phase we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in Figure~\ref{fig-training}), but our system works perfectly without it.
 Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Figure~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset. However, when we slightly modified the environment, the images displaying the text with a different shade and size, none of the features were successfully extracted, and the network outputted white noise (see Figure~\ref{fig-train-single-4}).
 \begin{figure}
     \centering
     \subfigure[input from same environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_1.png}
         \label{fig-train-single-1}
         }
     \subfigure[output of (a)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_2.png}
         \label{fig-train-single-2}
         }
     \subfigure[input from different environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_5.png}
         \label{fig-train-single-3}
         }
     \subfigure[output of (c)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_4.png}
         \label{fig-train-single-4}
         }
     \subfigure[ground truth]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3.png}
         \label{fig-train-single-5}
         }
        \caption{Results of training with data collected in fixed environment. The network performs well in this environment but fails in other.}
        \label{fig-train-single}
\end{figure}

As a result of these observations, we have to collect images in varied environments. Our experiment consists of 2 smartphones, one for the attacker and one the victim. Their distance is between 1 and 2 meters for traditional lenses(for the camera of the attacker's phone) without optical zooming, and 5 to 7.5 meters for lenses with optical zooming. Both phones are fixed to stands to keep them completely still, but as mentioned above, the lenses with optical zoom will shift slightly time to time, which is similar to a handheld situation. An app runs inside the attacker's phone, taking photos continuously, adjusting its focus and aperture, trying it's best to capture high-quality photos. Another app runs inside the victim's phone, displaying random characters with several fonts and colors, for the attacker to capture. The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this assemble into training and testing subsets. As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters. As the experiment goes on, the attacker phone will keep on taking photos in burst mode (20 photos per time), and the victim phone will change the characters it is displaying at a fixed interval, when approximately 100 images were taken by the attacker. We change the environmental setting whenever about 2k photos were taken, relocating the phones (while keeping their distance between 1 and 2 meters) or modifying the angle of the phones. The attacker will always point its phone directly at the victim, keeping its screen in the middle of the photos; The victim, however, may tilt its phone at an angle within 30 degrees. We then readjust the focus and aperture of the attacker's phone to maximize the image quality before continuing data collection. Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation.

The data was collected indoors, as is often the case of shoulder-surfing in public areas (theaters, subways, offices, etc.). We perform the experiment in a room with a window and repeat the data collection phase in different times of the day and night, with curtains drawn or open, lights turned on and off to modify the illumination parameter. The position of the phones is also a crucial factor in this parameter, and we avoid having the sunlight directly shone on the camera of the attacker or the screen of the victim, as it is extremely difficult to see anything in these extreme circumstances. We also draw a box around the characters on the victim's screen for alignment purposes, as although in production our system can detect the edges of the screen for alignment, this method provides more accurate results and possibly accelerates training. After collecting the images, we crop them along these boxes, retaining only the characters. In the training phase we randomly crop out squares of 9x9 pixels at the corresponding position on the training dataset and ground truth, and feed them into the neural network. We collected 800,000 images in this way with a Redmi6A phone (which possess a camera with 130 million pixels). This process is extremely time-consuming, but the data amount is crucial in our experiment, as slight variations of the environment will cause drastic changes in the features extracted from the characters, and only by covering the variations in each of the environmental parameters in the training data can the system successfully function in different scenarios.

>>>>

\subsection{Data Collection}
\label{sec-experiment-setting}

In our experiment, we are forced to collect the training dataset on our own instead of using public datasets. Because of our unique application, to the best of our knowledge there is no publicly available image dataset built for shoulder-surfing. Modern network architectures work with naturally obtained images, e.g. ordinary photos, satellite images, scanned documents, YouTube videos, etc. where the images are well focused and captured within the imaging ability of the camera, with the objects of interest, e.g. the face or the printed word, at least visible to the naked eye. and we apply the SR algorithms to reduce noise and refine details, like repainting texture and refining edges. However, as emphasized above, in our application we face images that is extremely blurred and distorted, due to the extreme circumstances when the photos are taken, and it is impossible to tell from each single picture whether a stroke of a character really belongs here, as it's equally possible that this line is a distorted mixture of multiple lines or is a mutilated part of a longer stroke. These are the reasons why our work does not choose datasets that are publicly available, and collect data by ourselves--as it will completely defeat the purpose if we turn to these datasets. And this also explains why we failed in trying to get comparable results with other SR architectures we use as baselines, as these networks are designed for another purpose and they hardly ever faced such distorted and blurred images.

The task of data collection is quite tedious, as we discovered that we need photos taken in all kinds of environments to train a robust network. We initially collect 60,000 images with the position of the smartphones static and all other environmental parameters stationary, and divided it into training and testing datasets which do not have common characters between them. Note that different lenses have different photographing abilities and blurring patterns, so the model has to be trained for each phone model. When using smartphones with optical zoom, the images will shift slightly time after time even if we keep them completely still, so the aligning phases are still needed (this shifting is also beneficial in that it simulates normal hand tremors in real-life scenarios even if we fix the phone to a stand instead of holding it up throughout the data collection phase which can last several hours). There are no consistency between adjacent images, so we also shuffle the images to increase this shifting effect and increase the variety of the training data. %To reduce calculation and better align the images with the ground truth, in the training data collection phase we drew a box around the text on the victim's screen, replacing the edges of the phone for alignment and cropping in the alignment step (as shown in Figure~\ref{fig-training}), but our system works perfectly without it.

Our network easily learned the patterns and presented equally satisfactory results in the test dataset (see Figure~\ref{fig-train-single-2}), displaying clean, easy to read results, showing that the network has learned to extract features beneath the character level, and it is highly possible that this network can recover all kinds of characters, not limited to the characters in the training dataset. However, when we slightly modified the environment, the images displaying the text with a different shade and size, none of the features were successfully extracted, and the network outputted white noise (see Figure~\ref{fig-train-single-4}).
 \begin{figure}
     \centering
     \subfigure[input from same environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_1.png}
         \label{fig-train-single-1}
         }
     \subfigure[output of (a)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_2.png}
         \label{fig-train-single-2}
         }
     \subfigure[input from different environment]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_5.png}
         \label{fig-train-single-3}
         }
     \subfigure[output of (c)]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_4.png}
         \label{fig-train-single-4}
         }
     \subfigure[ground truth]{
         \includegraphics[width=0.2\textwidth]{pic/training_single_dataset_3.png}
         \label{fig-train-single-5}
         }
        \caption{Results of training with data collected in fixed environment. The network performs well in this environment but fails in other.}
        \label{fig-train-single}
\end{figure}

\subsection{Experiment Setting}
As a result of these observations, we have to collect images in varied environments. Our experiment consists of 2 smartphones, one for the attacker and one the victim. Their distance is between 1 and 2 meters for traditional lenses(for the camera of the attacker's phone) without optical zooming, and 5 to 7.5 meters for lenses with optical zooming. Both phones are fixed to stands to keep them completely still, but as mentioned above, the lenses with optical zoom will shift slightly time to time, which is similar to a handheld situation. An app runs inside the attacker's phone, taking photos continuously, adjusting its focus and aperture, trying it's best to capture high-quality photos. Another app runs inside the victim's phone, displaying random characters with several fonts and colors, for the attacker to capture. The characters are selected from commonly used Chinese characters with 5 to 10 strokes and the English alphabet, and we divide this assemble into training and testing subsets. As the English characters are apparently easier to classify and reconstruct for the networks, the experiments testing the performance of the network will be performed only on Chinese characters, but it is our observation that our system works on English characters as well as Chinese characters.

As the experiment goes on, the attacker phone will keep on taking photos in burst mode (20 photos per time), and the victim phone will change the characters it is displaying at a fixed interval, when approximately 100 images were taken by the attacker. We change the environmental setting whenever about 2k photos were taken, relocating the phones (while keeping their distance between 1 and 2 meters) or modifying the angle of the phones. The attacker will always point its phone directly at the victim, keeping its screen in the middle of the photos; The victim, however, may tilt its phone at an angle within 30 degrees. We then readjust the focus and aperture of the attacker's phone to maximize the image quality before continuing data collection. Screenshots were taken in the victim's phone each time it changes its display, and these screenshots are scaled, spun and deformed according to the distance and angle between the phones at the time, and used as ground truth for training and evaluation.

The data was collected indoors, as is often the case of shoulder-surfing in public areas (theaters, subways, offices, etc.). We perform the experiment in a room with a window and repeat the data collection phase in different times of the day and night, with curtains drawn or open, lights turned on and off to modify the illumination parameter. The position of the phones is also a crucial factor in this parameter, and we avoid extreme settings, e.g. having the sunlight directly shining on the screen. We collected 800,000 images in this way with a Redmi6A phone (which possess a camera with 130 million pixels). This process is extremely time-consuming, but the data amount is crucial in our experiment, as slight variations of the environment will cause drastic changes in the features extracted from the characters, and only by covering the variations in each of the environmental parameters in the training data can the system successfully function in different scenarios.

### 2020-06-30 introduction.tex
修改

\cl{Evaluations can be summarized here (performance and comparison with existing works).}

\vspace{1mm}
\noindent
\textbf{Summary of Evaluation Results.}

>>>>

\vspace{1mm}
\noindent
\textbf{Summary of Evaluation Results.}
Equipped with our uniquely designed SR algorithm, our system can help the attacker read the characters shown on the victim's phone with above 90\% accuracy at 2m distance on a smartphone without optical zooming, or 6m distance on a phone with optical zooming in our experimental settings. The system is able to capture photos and produce high-res images constantly with about 2 seconds interval. Our experiments with real life scenarios show that this system is able to decipher texts or passwords of the victim at a safe distance, without alarming the victim, posing a threat to screen privacy.

### 2020-06-30 related_work.tex
修改

\subsection{Super Resolution}
Image super-resolution is the process of reconstructing an image with a higher spatial resolution. Single image super-resolution techniques accept a single low-res image as input, and based on its structural pattern, self-similarity \cite{suetake2008image}, or previous knowledge of the genre of the image, deduces missing information and reconstructs the missing pixels to form a sharp, high-res image. On the other hand, multiple image super-resolution techniques work on a set of pictures on the same scene, e.g. multiple snapshots captured by the camera of a smartphone, successive images from a satellite, or adjacent frames on a video clip. Although they picture the same scene and are mostly identical to each other, those low-res pictures can be viewed as replicas of a certain high-res scene with random pixels blurred and removed, and multiple image super-resolution algorithms reconstruct the high-res scene by merging these incomplete information sources, often exhibiting better performance than single image super-resolution.

As mentioned above, multiple image super-resolution algorithms are based on the assumption that all input images are reflections of the same scene. It can be assumed that there exists a high-res image H, and each input low-res image Li is a version of an aliased, blurred, downsampled and noised H. By modelling the alias, blur and noise effects, and comparing these low-res inputs, we can grasp an estimation of those degrading effects and neutralize them, and the output of our super-resolution algorithm will be a high-res image H’ with the most possibility to single-handedly generate all the input images Li via the aliasing, blurring, downsampling and noising processes.

Over the last two decades a variety of techniques have been proposed for the multiple image super-resolution problem. Early works focus on the analysis of the images on frequency or special domains, focusing on their pixel level differences and merging their information. Spatial domain methods mostly work on the interpolation approach, trying to insert new pixels between pixels of the low-res images. One of the well-known methods in the spatial domain is the Shift-Add algorithm \cite{farsiu2003robust}, which functions by maximizing the pixel-wise possibility of high-res image generating low-res images with gradient decent methods. On the other hand, frequency domain approaches focus on the Fourier transform of the images, and reconstruct high-res images based on patterns of the images in the frequency domain. Downsampling processes remove high-frequency components of the images, preserving low-frequency components; Noises often exists in a certain frequency band and can thus be identified and removed. By assuming that the high-res scene is band-limited, with CFT and DFT transformations, frequency domain algorithms can reconstruct high-frequency components from patterns of the low-frequency components, removing bands of noise and blur effects at the same time. A great variety of techniques have been proposed, however, due to the nature of the problem, these algorithms are all tailored for their application: natural photos, scanned text, satellite imaging, biometrics, etc. and achieve best performance only in their own field.

More recent works of Super Resolution are often based on deep learning approaches. In 2016, SRCNN \cite{dong2015image} was developed from CNN replacing pooling layers with upsampling layers, achieving notably better performance than previous approaches. This work focuses on single image super-resolution, as the neural network accepts a single image as input. As Generative Adversarial Networks (GAN) were proposed, the network good at constructing images pleasant to the human eye was also introduced into the domain of super resolution \cite{ledig2017photo}. These networks generate photo-realistic images, with less artifacts and more genuine-looking details pleasing to the human eye, though not always accurate against the real scene. Note that super resolution is an ill-posed problem, that is, we do not have a ‘ground truth’ to begin with, and traditional evaluation methods, e.g. mean square error (MSE) might not be suitable according to the application. Although SRGAN might score slightly lower on MSE, it can reconstruct more high-frequency and realistic details and score much higher on the mean opinion score (MOS). However, when published, the above works were limited to single input images. Because of increasing complexity and training difficulty, we cannot directly modify these super resolution neural networks to accept multiple images as input. There are also various works adapting neural networks to perform multi-image SR tasks. The most common variation is video SR\cite{shi2016real, kappeler2016video}, accepting complete video clips as input, and functioning on the similarity between frames. The sequentiality and consistency between adjacent frames makes it easy for the convolution networks to comprehend, and by modifying the 2d convolution layers to 3d convolution\cite{caballero2017real}, modifying the dataflow to merge neighboring frames among the network layers\cite{huang2017video}, or recurrently processing the frames under the guidance of the output of the previous frame\cite{sajjadi2018frame}, the task can be completed easily. Other works face image groups without consistency or sequential information, e.g. satellite images. To achieve appreciable results, most works choose hybrid methods, solving the multi-image SR problem with multiple single-image SR procedures. They commonly function by merging the results of single image SR algorithms to efficiently utilize input information\cite{kawulok2019deep}, or building a multi-image network to create a course view and support it with single image SR networks\cite{8834937}. These methods expect at least some degree of information to be extracted from each of the single frames with single image SR methods.

However, the methods mentioned above are not suitable for our application and we need a novel approach. The blurriness of our photos exceeds the processing ability of non-learning methods; furthermore, these photos are extremely blurred, defocused and full of noise so that few information can be extracted from them via single image SR methods; The adjacent frames display drastically different blurring patterns so that they lack consistency between adjacent frames. Only from an overall view of all the images can we distinguish noise from facts, and we need a network that can comprehend the similarities and differences between each frame to recover the buried information, and indeed, building an end-to-end multi-image SR network without assuming sequential consistency between frames is still a very much underexplored field of study, and our work aims at filling that gap.

>>>>

\subsection{Super Resolution}
Image super-resolution is the process of reconstructing an image with a higher spatial resolution. Single image super-resolution techniques accept a single low-res image as input, and based on its structural pattern, self-similarity \cite{suetake2008image}, or previous knowledge of the genre of the image, deduces missing information and reconstructs the missing pixels to form a sharp, high-res image. On the other hand, multiple image super-resolution techniques work on a set of pictures on the same scene, e.g. multiple snapshots captured by the camera of a smartphone, successive images from a satellite, or adjacent frames on a video clip. These algorithms collect extra data from slight differences of these redundant images, often exhibiting better performance than single image super-resolution.

Over the last two decades a variety of techniques have been proposed for the multiple image super-resolution problem. Early works focus on the analysis of the images on spatial or frequency domains. One of the widely known spatial domain methods is the Shift-Add algorithm \cite{farsiu2003robust}, which functions by maximizing the pixel-wise possibility of high-res image generating low-res images. On the other hand, frequency domain approaches focus on the Fourier transform of the images. By assuming that the high-res scene is band-limited, frequency domain algorithms can reconstruct high-frequency components from patterns of the low-frequency components, removing bands of noise and blur effects at the same time. A great variety of techniques have been proposed, however, due to the nature of the problem, these algorithms are all tailored for their application: natural photos, scanned text, satellite imaging, biometrics, etc. and achieve best performance only in their own field.

More recent works of Super Resolution are often based on deep learning approaches. In 2016, SRCNN \cite{dong2015image} was developed from CNN replacing pooling layers with upsampling layers, achieving notably better performance than previous approaches. This work focuses on single image super-resolution, as the neural network accepts a single image as input. Generative Adversarial Networks (GAN) were also used in this era\cite{ledig2017photo}, generating photo-realistic images, with less artifacts and more genuine-looking details pleasing to the human eye, though not always accurate against the real scene. When published, the above works were limited to single input images, and most multi-image SR tasks are variations of them. The most common variation is video SR\cite{shi2016real, kappeler2016video}, with a structure similar to SRCNN, accepting complete video clips as input, and functioning on the similarity between frames. The sequentiality and consistency between adjacent frames makes it easy for the convolution networks to comprehend, and by modifying the 2d convolution layers to 3d convolution\cite{caballero2017real}, modifying the dataflow to merge neighboring frames among the network layers\cite{huang2017video}, or recurrently processing the frames under the guidance of the output of the previous frame\cite{sajjadi2018frame}, the task can be completed easily. Other works face image groups without consistency or sequential information, e.g. satellite images. To achieve appreciable results, most works choose hybrid methods, solving the multi-image SR problem with multiple single-image SR procedures. They commonly function by merging the results of single image SR algorithms to efficiently utilize input information\cite{kawulok2019deep}, or building a multi-image network to create a course view and support it with single image SR networks\cite{8834937}. These methods expect at least some degree of information to be extracted from each of the single frames with single image SR methods. However, because of the extreme blurriness of the photos and the lack of consistency between frames, the methods mentioned above are not suitable for our application and we need a novel approach.
